A First Effort for a Distributed Segment-based Approach on Self-Assembled Nano Networks

### 2014-02-14 PAPER/implementation.tex
implementation new update

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{pictures/packager.eps}
  \caption{Packager block}
 \label{fig:packager}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{pictures/pipeline.eps}
  \caption{Pipeline description of \disr{} operations}
 \label{fig:pipeline}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.50\textwidth]{pictures/synthesis.eps}
  \caption{Number of network's node (N) vs number of CNFETs necassary to implement
  the \disr{} circuitry.}
 \label{fig:synthesys}
\end{figure}

@@

In order to have an idea of the maximum working clock frequency for
the implemented circuitry, timing results can be obtained from a gate-
level netlist. Since a complete technology library usefull for
commercial synthesis tool (like Design Compiler) doesn't exist for 
this particular technology (at the best that we know), we have
synthesized the RTL description of \disr{} with a standard 32nm CMOS
library obtaining  a delay of about $\mathrm{\tau_{\disr{}}=10} FO4$
(fan-out of four). Considering the results obtained
in~\cite{deng_isscc07}, wich reports the ratio in therms of FO4
between a standard 32nm CMOS technology and a carbon nanotube ones, 
rough delay estimation can be obtained. In particolar has been reported a
ratio R of:  
\begin{equation}
\mathrm{R=\frac{FO4_{CMOS}}{FO4_{CNFET}}=2}  
\end{equation}
Considering that F04 CMOS is about 30 ps, and the results of last
equation, a FO4 for the CNFET case is equal to about 15 ps, and
then the working frequency can be computed as:
\begin{equation}
\mathrm{f_{clk}=\frac{1}{T_{max}}=\frac{1}{\tau_{\disr{}} \cdot FO4_{CNFET}}}=
\frac{1}{10\cdot 15 \cdot 10^{-12}}=6,6 GHz
\end{equation}
where $\mathrm{\tau_{\disr{}}}$ was expressed in therms of FO4.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{pictures/packager.eps}
  \caption{Packager block.}
 \label{fig:packager}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{pictures/pipeline.eps}
  \caption{Pipeline description of \disr{} operations.}
 \label{fig:pipeline}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.50\textwidth]{pictures/synthesis.eps}
  \caption{Network size vs number of CNFETs necassary to implement
  the \disr{} circuitry.}
 \label{fig:synthesys}
\end{figure}

@@

In order to have an idea of the maximum working clock frequency for
the implemented circuitry, timing results can be obtained from a 
gate-level netlist. Since a complete technology library usefull for
commercial synthesis tool (like Design Compiler) doesn't exist for 
this particular technology (at the best that we know), we have
synthesized the RTL description of \disr{} with a standard 32 nm CMOS
library obtaining  a delay of about $\mathrm{\tau_{\disr{}}=10} \ FO4$
(fan-out of four). Considering the results obtained
in~\cite{deng_isscc07}, wich reports the ratio in therms of FO4
between a standard 32 nm CMOS technology and a carbon nanotube ones, 
rough delay estimation can be obtained. In particolar in such work 
has been reported a ratio of:  
\begin{equation}
\mathrm{\frac{FO4_{CMOS}}{FO4_{CNFET}}=2}  
\end{equation}
Considering that F04 CMOS is about 30 ps, and the results of last
equation, a FO4 for the CNFET case is equal to about 15 ps, and
then the working frequency can be computed as:
\begin{equation}
\mathrm{f_{clk}=\frac{1}{T_{max}}=\frac{1}{\tau_{\disr{}} \cdot FO4_{CNFET}}}=
\frac{1}{10\cdot 15 \cdot 10^{-12}}=6,6 GHz
\end{equation}
where $\mathrm{\tau_{\disr{}}}$ was expressed in therms of FO4.
